---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE,include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
require(glm2, quietly = TRUE)
```

# glm2

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/glm2)](https://cran.r-project.org/package=glm2)

`glm2` fits generalized linear models using the same model specification as `glm` in the `stats` package, but with a modified default fitting method. The method provides greater stability for models that may fail to converge using `glm`.

## Example

An example of periodic non-convergence using `glm`:

```{r}
require(glm2, quietly = TRUE)
data(crabs)

fit1 <- glm(Satellites ~ I(Width - min(Width)) + factor(Dark) + factor(GoodSpine),
            family = poisson(link = "identity"), start = rep(1, 4),
            data = crabs, subset = Rep1, trace = TRUE)
```

The same model converges successfully with `glm2`:

```{r}
fit2 <- glm2(Satellites ~ I(Width - min(Width)) + factor(Dark) + factor(GoodSpine),
             family = poisson(link = "identity"), start = rep(1, 4),
             data = crabs, subset = Rep1, trace = TRUE)

noquote(c("deviances: ", fit1$deviance, fit2$deviance))
noquote(c("converged: ", fit1$converged, fit2$converged))
```

## Installation

Get the released version from CRAN:

```{r, eval = FALSE}
install.packages("glm2")
```

Or the development version from github:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdonoghoe/glm2")
```

## References

* Marschner, I. C. (2011). glm2: Fitting generalized linear models with convergence problems. _The R Journal_ **3**(2): 12--15.